\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2019-07-30 paper/sp.tex

Because of our train-and-test framework, each star is given a spectrophotometric
parallax based on coefficients derived from training on a complementary Training Set sample, of
which that star is not a member.
As we emphasize above, this also ensures that the \gaia\ measurement $\gparallax_m$ of star $m$ is never used,
even indirectly, in generating the spectrophotometric estimate $\sparallax_m$ for that star $m$.
This, in turn, ensures statistical independence of the
parallax estimates generated here from the \gaia\ parallaxes.
The two could even be combined na\"ively in an inference.

@@

\bibitem[Eilers \etal(2018)]{eilers} Eilers,~A.~C., Hogg, D.~W., Rix, H.-W., \& Ness, M. 2018, in preparation

>>>>

Because of our train-and-test framework, each star is given a spectrophotometric
parallax based on coefficients derived from training on a complementary Training Set sample, of
which that star is not a member.
As we emphasize above, this ensures that the \gaia\ measurement $\gparallax_m$ of star $m$ is never used,
even indirectly, in generating the spectrophotometric estimate $\sparallax_m$ for that star $m$.
This leads to true statistical independence of the
parallax estimates generated here from the \gaia\ parallaxes.
The two could even be combined na\"ively in an inference.

@@

\bibitem[Eilers \etal(2018)]{eilers} Eilers,~A.~C., Hogg, D.~W., Rix, H.-W., \& Ness, M. 2019, \apj, 871, 120
